Effects of Reynolds Number on the Energy Conversion and Near-Wake Dynamics of a High Solidity Vertical-Axis Cross-Flow Turbine

### 2015-10-12 paper.tex
Adjust caption
Lift and drag coefficient notation formatting

Hydro- or airfoil section performance is generally characterized by the
lift-to-drag force ratio $L/D$  (or lift vs drag coefficient, $c_L/c_D$ ), which
is primarily a function of the foil's angle of attack $\alpha$. The angles of
attack for cross-flow turbine blades are a function of turbine tip speed ratio,
induction (slowing/turning of the free stream flow prior to reaching the
turbine), and turbine rotation or azimuthal angle $\theta$. Looking at static
airfoil data, we see that the static stall angle---the angle just beyond that at
which $L/D$ is maximum---increases with blade chord Reynolds number $Re_c$
\cite{Jacobs1937}.

@@

\caption{Airfoil lift to drag ratio as a function of Reynolds number, from
\cite{McMasters1980}.}

>>>>

Hydro- or airfoil section performance is generally characterized by the
lift-to-drag force ratio $L/D$  (or lift vs drag coefficient, $C_l/C_d$ ), which
is primarily a function of the foil's angle of attack $\alpha$. The angles of
attack for cross-flow turbine blades are a function of turbine tip speed ratio,
induction (slowing/turning of the free stream flow prior to reaching the
turbine), and turbine rotation or azimuthal angle $\theta$. Looking at static
airfoil data, we see that the static stall angle---the angle just beyond that at
which $L/D$ is maximum---increases with blade chord Reynolds number $Re_c$
\cite{Jacobs1937}.

@@

\caption{Airfoil maximum lift to drag ratio versus Reynolds number, from
    \cite{McMasters1980}.}
